---
title: "rsv_inter_ew"
author: "David Hodgson"
date: "24/09/2020"
output: html_document
---


# 1. Setup 
# 1.1 Import libraries
May need to downoad all of these (use install.packages)
```{r libraries}

library(Rcpp)       # For c++ intergration
library(RcppEigen)  # Ditto
library(coda)       # Ditto
library(tidyverse)
library(parallel)
library(MASS)
library(foreach)
library(gridExtra)
library(doParallel)
library(BayesianTools)
library(devtools)
library(here)
library(patchwork)
source( here("R", "gen_data", "helpers.R")) #ensure c++14 is enabled

```


## 2 Import data for the epidemic model intervention model
### 2.1 RunIntervention class

This section calls a class from the cpp module inteface (RunInterventions.cpp) for the cpp intervention model (defined in RunInterventions.h).
Then, using demographic data from the UK (ukdata) and model data needed for the intervention programmes (data_inter_uk), the intervention model class is initialised and ready to use! 

```{r}


# Load premade datasets
load(file = here::here("data", "inputs", "rsv_data_resceu.RData")) # loads resceudata
load(file = here::here("data", "inputs", "inter_data_uk.RData")) # loads data_inter_uk
load(file = here::here("data", "inputs", "prior_data_resceu.RData"))   # Load in model data, including observation data (which is made up i.e. not the same as I used in the paper).

sourceCpp(here("src", "RunInterventions.cpp")) # Uploads empty RunInterventions class
source(here("R", "RunInterventionsClass.R")) # Uploads emmake_RunInterventionspty function
classRunInterventions <- make_RunInterventions(RunInterventions, resceudata, data_inter_uk, 30 * 12 + 1, 30 * 12)


sourceCpp(here("src", "logLikelihoodModule.cpp")) #ensure c++14 is enabled
classEvaluateLogLikelihood <- new(EvaluateLogLikelihood, resceudata$numberDailyLiveBirths, resceudata$population, resceudata$ageGroupBoundary) # Calls class
classEvaluateLogLikelihood$contactMatrixPhy <- t(resceudata$contactMatrixPhy)
classEvaluateLogLikelihood$contactMatrixCon <- t(resceudata$contactMatrixCon)
classEvaluateLogLikelihood$observedData <- as.matrix(resceudata$observationalData)
classEvaluateLogLikelihood$lowerParamSupport <- priordata$fit.par$lowerParSupport
classEvaluateLogLikelihood$upperParamSupport <- priordata$fit.par$upperParSupport
classEvaluateLogLikelihood$run_start <- 0
classEvaluateLogLikelihood$run_burn <- 0
classEvaluateLogLikelihood$run_oneyr <- 30 * 12 + classEvaluateLogLikelihood$run_burn
classEvaluateLogLikelihood$run_full <- 30 * 12 # number of days to fit the data and model to

```

# 3. Code to run custom RSV intervention programmes

Three examples of how to implement your own custom calendars are given below. 

```{r}

source("R/vac_cal.R") # generates the vaccination calendars
source("R/calc_outcomes.R")  # calculate the outcomes
load(here("data", "posteriors_resceu.RData"))  # posteriors from fitting in previous RMarkdown
post_sample <- output1[[1]][[1]][1, ]
state_var_v1 <- classEvaluateLogLikelihood$getDebug(post_sample)

make_vac_program_info_custom_P0 <- function(seed) {
  list(
      pal = list(id = TRUE, age_id = rep(0, 25), t_start = 14, t_end = 14 + 30, eff = 0.5, cov = 0.0)
    )
}

func <- make_vac_program_info_custom_P0(1)

vac_cal <- create_calendar(func, "week", 0)
cal <- get_cal(vac_cal)
dose <- get_dose(vac_cal)
vac_par_info <- list(om_mab = 1 / 150, direct = FALSE, xi_boost = 1)

state_var_v2 <- classRunInterventions$getDebug(cal, dose, vac_cal[["cov_c"]], vac_par_info, post_sample)

compare_outputs(state_var_v1, state_var_v2, 300)

```

```{r}

compare_outputs <- function(state_var_v1, state_var_v2, t) {
  name <- c("M", "S1", "E1", "A1", "I1", "R1", "S2", "E2", "A2", "I2", "R2", "S3", "E3", "A3", "I3", "R3", "S4", "E4", "A4", "I4", "R4")
  ll = 1:21 %>% map(~state_var_v1[t, ][seq(.x, 23*25, 23)]) %>% unlist
  ri = lapply(1:21, function(y) (1:25 %>% map(~sum(state_var_v2[t, ][seq(y + 455*(.x - 1), 24*9 + 455*(.x - 1), 24)])) %>% unlist)) %>% unlist

  data.frame( 
    name = 1:21 %>% map(~rep(name[.x], 25)) %>% unlist,
    ag = rep(1:25, 21),
    ll = ll,
    ri = ri
  ) %>%
  mutate(dif = ll - ri)
}


```