---
title: "rsv_inter_ew"
author: "David Hodgson"
date: "24/09/2020"
output: html_document
---


# 1. Setup 
# 1.1 Import libraries
May need to downoad all of these (use install.packages)
```{r libraries}

library(Rcpp)       # For c++ intergration
library(RcppEigen)  # Ditto
library(coda)       # Ditto
library(tidyverse)
library(parallel)
library(MASS)
library(foreach)
library(gridExtra)
library(doParallel)
library(BayesianTools)
library(devtools)
library(here)
library(patchwork)
source( here("R", "gen_data", "helpers.R")) #ensure c++14 is enabled

```


## 2 Import data for the epidemic model intervention model
### 2.1 RunIntervention class

This section calls a class from the cpp module inteface (RunInterventions.cpp) for the cpp intervention model (defined in RunInterventions.h).
Then, using demographic data from the UK (ukdata) and model data needed for the intervention programmes (data_inter_uk), the intervention model class is initialised and ready to use! 

```{r}

sourceCpp(here("src", "RunInterventions.cpp")) # Uploads empty RunInterventions class
source(here("R", "RunInterventionsClass.R")) # Uploads emmake_RunInterventionspty function
burnin_yrs <- 2
run_yrs <- 5

# Load premade datasets
load(file = here::here("data", "inputs", "rsv_data_resceu.RData")) # loads resceudata
load(file = here::here("data", "inputs", "inter_data_uk.RData")) # loads data_inter_uk

classRunInterventions <- make_RunInterventions(RunInterventions, resceudata, data_inter_uk, 30 * 12 + 1, 30 * 12 * 10)

```

# 3. Code to run custom RSV intervention programmes

Three examples of how to implement your own custom calendars are given below. 

```{r}

# Load relevant R scripts
source("R/vac_cal.R") # generates the vaccination calendars
source("R/calc_outcomes.R")  # calculate the outcomessource
source("R/cal_risks.R")  # calculate the outcomes

# Load posteriors
load(here("data", "posteriors_resceu_alt.RData"))  # posteriors from fitting in previous RMarkdown
# Load seeds
seeds <- read.csv(here("data", "inputs", "seed_samples.csv"), header = FALSE)[, 1] + 1

#fit_vals_beta(c(0.2, 0.44, 0.62)) # mat efficacy (infants)
#fit_vals_beta(c(0.2, 0.44, 0.62)) # mat efficacy (infants)
#fit_vals_beta(c(0.519, 0.784, 0.903)) # mab efficacy
#fit_vals_beta(c(0.05, 0.39, 0.64)) # lav efficacy

ind_pal <- c(rep(1, 9), rep(0, 16)) # VHR (<8 months)
ind_mabs <- c(rep(1, 1), rep(0, 24)) # Birth only (0 months only)
mat_eff <- rbeta(1250,   8.333082, 11.650052) # efficacy of materal antibodies
mab_eff <- rbeta(1250, 12.462339,  4.079271) # efficacy of long-acting mabs
lav_eff <- rbeta(1250, 3.24646, 5.997432) # efficacy of long acting monoclonal antibodies

ind_parents <- c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1.0,1.0,1.0,0,0,0,0) # 15-44 (parents)
u6mo <- c(1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0) # 15-44 (parents)

# VHR, HR and LR at birth during the winter

```

## Comparator
```{r}

source("R/vac_cal.R") # generates the vaccination calendars
source("R/calc_outcomes.R")  # calculate the outcomessource
source("R/cal_risks.R")  # calculate the outcomes
source("R/cea.R")


xi_days_boost <- 90
vac_par_info <- list(om_mab = 1 / 150, direct = FALSE, xi_boost = 60 / xi_days_boost)

make_vac_program_info_custom_None <- function(seed) {
  list(

    )
}

outputNone <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.0, output1[[1]][[1]], 0, 0.03, 1)
cal_risks(outputNone, resceudata)
outputNone <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.0, output1[[1]][[1]], 0, 0.03, 1)

# outputNone
outputNone_67 <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.67, output1[[1]][[1]], 0, 0.03, 1)
outputNone_44 <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.44, output1[[1]][[1]], 0, 0.03, 1)
outputNone_03 <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.03, output1[[1]][[1]], 0, 0.03, 1)
outputNone_70 <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.70, output1[[1]][[1]], 0, 0.03, 1)

outputNoneHigh <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.67, output1[[1]][[1]], 0, 0.03, 1.5)
outputNoneLow <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_None, vac_par_info, 0.67, output1[[1]][[1]], 0, 0.03, 0.5)

save(outputNone, file = here::here("outputs", "burden_full", "none.RData") )
save(outputNone_67, file = here::here("outputs", "burden_full", "none_67.RData") )
save(outputNone_44, file = here::here("outputs", "burden_full", "none_44.RData") )
save(outputNone_03, file = here::here("outputs", "burden_full", "none_03.RData") )
save(outputNone_70, file = here::here("outputs", "burden_full", "none_70.RData") )

save(outputNoneLow, file = here::here("outputs", "burden_full", "none_low.RData") )
save(outputNoneHigh, file = here::here("outputs", "burden_full", "none_high.RData") )

none_final <- save_outputs(outputNone, "no_inter")
save_excel(none_final, "burden_no_inter")

none_final_67 <- save_outputs(outputNone_67, "no_inter_67")
none_final_44 <- save_outputs(outputNone_44, "no_inter_44")
none_final_03 <- save_outputs(outputNone_03, "no_inter_03")
none_final_70 <- save_outputs(outputNone_70, "no_inter_70")

none_final_low <- save_outputs(outputNoneLow, "no_inter_low")
none_final_high <- save_outputs(outputNoneHigh, "no_inter_high")

```

## Maternal vaccination stuff

```{r}

vac_par_info <- list(om_mab = 1 / 150, direct = FALSE, xi_boost = 60 / xi_days_boost)

make_vac_program_info_custom_none_mat <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 52, eff_inf = 0.39, eff_mat = lav_eff[seed], cov = 0.0)
    )
}

make_vac_program_info_custom_Base <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 52, eff_inf = 0.39, eff_mat = lav_eff[seed], cov = 0.67)
    )
}

make_vac_program_info_custom_P1 <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 21 + 1, eff_inf = 0.39, eff_mat = lav_eff[seed], cov = 0.44)
    )
}

make_vac_program_info_custom_P3 <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 21 + 1, eff_inf = 0.39, eff_mat = lav_eff[seed], cov = 0.30)
    )
}

# Ex.2a Long-acting monoclonal antibodies at HR, LR, and VHR, given seasonally (Oct to April) at birh ONLY with 98% coverage (cannot include manual duration of protection) PLUS
# Ex.2b Maternal vaccination given seasonally (July to Jan to prevent infections in Oct to April) with 70% coverage. Average duration of protection is 150 days.
# VHR, HR and LR at birth during the winter
#vac_program_info_custom <- make_vac_program_info_custom_P8(1)
#vac_cal <- create_calendar(vac_program_info_custom, "week", 0.6)


make_vac_program_info_custom_P4 <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 21 + 1, eff_inf = 0.39, eff_mat = lav_eff[seed], cov = 0.70)
    )
}

make_vac_program_info_custom_P5 <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 52, eff_inf = 0.05, eff_mat = lav_eff[seed], cov = 0.67)
    )
}

make_vac_program_info_custom_P6 <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 52, eff_inf = 0.6, eff_mat = lav_eff[seed], cov = 0.67)
    )
}

make_vac_program_info_custom_P7 <- function(seed) {
  list(
      mat =  list(id = TRUE, age_id = ind_parents, t_start = 1, t_end = 52, eff_inf = mat_eff[seed], eff_mat = lav_eff[seed], cov = 0.67)
    )
}

none_mat <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_none_mat, vac_par_info, 0.0, output1[[1]][[1]], 0, 0.03, 1)
outputBase_mat <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.67, output1[[1]][[1]], 200000, 0.03, 1)
outputP1_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P1, vac_par_info, 0.44, output1[[1]][[1]], 100000, 0.03, 1)
outputP3_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P3, vac_par_info, 0.30, output1[[1]][[1]], 100000, 0.03, 1)
outputP4_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P4, vac_par_info, 0.70, output1[[1]][[1]], 100000, 0.03, 1)
outputP5_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P5, vac_par_info, 0.67, output1[[1]][[1]], 200000, 0.03, 1)
outputP6_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P6, vac_par_info, 0.67, output1[[1]][[1]], 200000, 0.03, 1)
vac_par_info <- list(om_mab = 1 / 150, direct = FALSE, xi_boost = 60 / 60)
outputP7_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.67, output1[[1]][[1]], 200000, 0.03, 1)
vac_par_info <- list(om_mab = 1 / 150, direct = FALSE, xi_boost = 60 / 180)
outputP8_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.67, output1[[1]][[1]], 200000, 0.03, 1)
vac_par_info <- list(om_mab = 1 / 150, direct = FALSE, xi_boost = 60 / xi_days_boost)
outputP9_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.67, output1[[1]][[1]], 200000, 0.03, 1.5)
outputP10_mat  <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.67, output1[[1]][[1]], 200000, 0.03, 0.5)


save(outputBase_mat, file = here::here("outputs", "burden_full", "Base_mat.RData") )
save(outputP1_mat, file = here::here("outputs", "burden_full", "P1_mat.RData") )
save(outputP3_mat, file = here::here("outputs", "burden_full", "P3_mat.RData") )
save(outputP4_mat, file = here::here("outputs", "burden_full", "P4_mat.RData") )
save(outputP5_mat, file = here::here("outputs", "burden_full", "P5_mat.RData") )
save(outputP6_mat, file = here::here("outputs", "burden_full", "P6_mat.RData") )
save(outputP7_mat, file = here::here("outputs", "burden_full", "P7_mat.RData") )
save(outputP8_mat, file = here::here("outputs", "burden_full", "P8_mat.RData") )
save(outputP9_mat, file = here::here("outputs", "burden_full", "P9_mat.RData") )
save(outputP10_mat, file = here::here("outputs", "burden_full", "P10_mat.RData") )

```


## MABs vaccination stuff

```{r}


make_vac_program_info_custom_Base <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 1, t_end = 52, eff = 0.701, cov = 0.94),
      mAB_HR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 1, t_end =  52, eff = 0.701, cov = 0.94),
      mAB_LR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 1, t_end =  52, eff = 0.701, cov = 0.94)
    )
}

make_vac_program_info_custom_P1 <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 14, t_end = 14 + 30, eff = 0.701, cov = 0.94),
      mAB_HR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.94),
      mAB_LR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.94)
    )
}

make_vac_program_info_custom_P2 <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 14, t_end = 14 + 30, eff = 0.701, cov = 0.94),
      mAB_HR =  list(id = TRUE, catchup = TRUE, age_id_catchup = u6mo, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.94),
      mAB_LR =  list(id = TRUE, catchup = TRUE, age_id_catchup = u6mo, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.94)
    )
}

# Ex.1a Long-acting monoclonal antibodies at HR, LR, and VHR, given seasonally (Oct to April) at birh ONLY with 43% coverage (cannot include manual duration of protection) PLUS
# Ex.1b Maternal vaccination given seasonally (July to Jan to prevent infections in Oct to April) with 31% coverage. Average duration of protection is 150 days.

make_vac_program_info_custom_P3 <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 14, t_end = 14 + 30, eff = 0.701, cov = 0.30),
      mAB_HR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.30),
      mAB_LR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.30)
    )
}

# Ex.2a Long-acting monoclonal antibodies at HR, LR, dand VHR, given seasonally (Oct to April) at birh ONLY with 98% coverage (cannot include manual duration of protection) PLUS
# Ex.2b Maternal vaccination given seasonally (July to Jan to prevent infections in Oct to April) with 70% coverage. Average duration of protection is 150 days.
# VHR, HR and LR at birth during the winter
#vac_program_info_custom <- make_vac_program_info_custom_P8(1)
#vac_cal <- create_calendar(vac_program_info_custom, "week", 0.6)

make_vac_program_info_custom_P4 <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 14, t_end = 14 + 30, eff = 0.701, cov = 0.70),
      mAB_HR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.70),
      mAB_LR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 14, t_end =  14 + 30, eff = 0.701, cov = 0.70)
    )
}

make_vac_program_info_custom_P5 <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 1, t_end = 52, eff = 0.52, cov = 0.94),
      mAB_HR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 1, t_end =  52, eff = 0.52, cov = 0.94),
      mAB_LR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 1, t_end =  52, eff = 0.52, cov = 0.94)
    )
}

make_vac_program_info_custom_P6 <- function(seed) {
  list(
      mAB_VHR = list(id = TRUE, age_id = ind_pal, t_start = 1, t_end = 52, eff = 0.812, cov = 0.94),
      mAB_HR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 1, t_end =  52, eff = 0.812, cov = 0.94),
      mAB_LR =  list(id = TRUE, catchup = FALSE, age_id = ind_mabs, t_start = 1, t_end =  52, eff = 0.812, cov = 0.94)
    )
}

outputBase_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 1)
outputP1_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P1, vac_par_info, 0.0, output1[[1]][[1]], 100000, 0.03, 1)
outputP2_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P2, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 1)
outputP3_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P3, vac_par_info, 0.0, output1[[1]][[1]], 100000, 0.03, 1)
outputP4_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P4, vac_par_info, 0.0, output1[[1]][[1]], 100000, 0.03, 1)
outputP5_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P5, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 1)
outputP6_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_P6, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 1)
vac_par_info <- list(om_mab = 1 / 120, direct = FALSE, xi_boost = 60 / xi_days_boost)
outputP7_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 1)
vac_par_info <- list(om_mab = 1 / 240, direct = FALSE, xi_boost = 60 / xi_days_boost)
outputP8_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 1)
vac_par_info <- list(om_mab = 1 / 150, direct = FALSE, xi_boost = 60 / xi_days_boost)
outputP9_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 1.5)
outputP10_mab <- run_sample_custom(seeds[1:100], make_vac_program_info_custom_Base, vac_par_info, 0.0, output1[[1]][[1]], 200000, 0.03, 0.5)


save(outputBase_mab, file = here::here("outputs", "burden_full", "Base_mab.RData") )
save(outputP1_mab, file = here::here("outputs", "burden_full", "P1_mab.RData") )
save(outputP2_mab, file = here::here("outputs", "burden_full", "P2_mab.RData") )
save(outputP3_mab, file = here::here("outputs", "burden_full", "P3_mab.RData") )
save(outputP4_mab, file = here::here("outputs", "burden_full", "P4_mab.RData") )
save(outputP5_mab, file = here::here("outputs", "burden_full", "P5_mab.RData") )
save(outputP6_mab, file = here::here("outputs", "burden_full", "P6_mab.RData") )
save(outputP7_mab, file = here::here("outputs", "burden_full", "P7_mab.RData") )
save(outputP8_mab, file = here::here("outputs", "burden_full", "P8_mab.RData") )
save(outputP9_mab, file = here::here("outputs", "burden_full", "P9_mab.RData") )
save(outputP10_mab, file = here::here("outputs", "burden_full", "P10_mab.RData") )

```

# Calculate the impact of the 11 different programmes 
## Mabs

```{r}

source(here::here("R/cea.R"))

# Run and save all for excel file
load(file = here::here("outputs", "burden_full", "none.RData") )
load(file = here::here("outputs", "burden_full", "none_high.RData") )
load(file = here::here("outputs", "burden_full", "none_low.RData") )

load(file = here::here("outputs", "burden_full", "Base_mab.RData") )
load(file = here::here("outputs", "burden_full", "P1_mab.RData") )
load(file = here::here("outputs", "burden_full", "P2_mab.RData") )
load(file = here::here("outputs", "burden_full", "P3_mab.RData") )
load(file = here::here("outputs", "burden_full", "P4_mab.RData") )
load(file = here::here("outputs", "burden_full", "P5_mab.RData") )
load(file = here::here("outputs", "burden_full", "P6_mab.RData") )
load(file = here::here("outputs", "burden_full", "P7_mab.RData") )
load(file = here::here("outputs", "burden_full", "P8_mab.RData") )
load(file = here::here("outputs", "burden_full", "P9_mab.RData") )
load(file = here::here("outputs", "burden_full", "P10_mab.RData") )

none_final <- save_outputs(outputNone, "no_inter")
base_mab_short <- save_outputs(outputBase_mab, "base_case_mab_short")
P1_mab_short <- save_outputs(outputP1_mab, "P1_case_mab_short")
P2_mab_short <- save_outputs(outputP2_mab, "P2_case_mab_short")
P3_mab_short <- save_outputs(outputP3_mab, "P3_case_mab_short")
P4_mab_short <- save_outputs(outputP4_mab, "P4_case_mab_short")
P5_mab_short <- save_outputs(outputP5_mab, "P5_case_mab_short")
P6_mab_short <- save_outputs(outputP6_mab, "P6_case_mab_short")
P7_mab_short <- save_outputs(outputP7_mab, "P7_case_mab_short")
P8_mab_short <- save_outputs(outputP8_mab, "P8_case_mab_short")
P9_mab_short <- save_outputs(outputP9_mab, "P9_case_mab_short")
P10_mab_short <- save_outputs(outputP10_mab, "P10_case_mab_short")

base <- none_final
programme <- base_mab_short

calc_impact(none_final, base_mab_short, "base_mab")
calc_impact(none_final, P1_mab_short, "P1_mab")
calc_impact(none_final, P2_mab_short, "P2_mab")
calc_impact(none_final, P3_mab_short, "P3_mab")
calc_impact(none_final, P4_mab_short, "P4_mab")
calc_impact(none_final, P5_mab_short, "P5_mab")
calc_impact(none_final, P6_mab_short, "P6_mab")
calc_impact(none_final, P7_mab_short, "P7_mab")
calc_impact(none_final, P8_mab_short, "P8_mab")
calc_impact(none_final_high, P9_mab_short, "P9_mab")
calc_impact(none_final_low, P10_mab_short, "P10_mab")
```

## Mats

```{r}

# Run and save all for excel file
load(file = here::here("outputs", "burden_full", "none.RData") )
load(file = here::here("outputs", "burden_full", "Base_mat.RData") )
load(file = here::here("outputs", "burden_full", "P1_mat.RData") )
load(file = here::here("outputs", "burden_full", "P3_mat.RData") )
load(file = here::here("outputs", "burden_full", "P4_mat.RData") )
load(file = here::here("outputs", "burden_full", "P5_mat.RData") )
load(file = here::here("outputs", "burden_full", "P6_mat.RData") )
load(file = here::here("outputs", "burden_full", "P7_mat.RData") )
load(file = here::here("outputs", "burden_full", "P8_mat.RData") )
load(file = here::here("outputs", "burden_full", "P9_mat.RData") )
load(file = here::here("outputs", "burden_full", "P10_mat.RData") )

none_final <- save_outputs(outputNone, "no_inter")
base_mat_short <- save_outputs(outputBase_mat, "base_case_mat_short")
P1_mat_short <- save_outputs(outputP1_mat, "P1_case_mat_short")
P3_mat_short <- save_outputs(outputP3_mat, "P3_case_mat_short")
P4_mat_short <- save_outputs(outputP4_mat, "P4_case_mat_short")
P5_mat_short <- save_outputs(outputP5_mat, "P5_case_mat_short")
P6_mat_short <- save_outputs(outputP6_mat, "P6_case_mat_short")
P7_mat_short <- save_outputs(outputP7_mat, "P7_case_mat_short")
P8_mat_short <- save_outputs(outputP8_mat, "P8_case_mat_short")
P9_mat_short <- save_outputs(outputP9_mat, "P9_case_mat_short")
P10_mat_short <- save_outputs(outputP10_mat, "P10_case_mat_short")

calc_impact(none_final_67, base_mat_short, "base_mat")
calc_impact(none_final_44, P1_mat_short, "P1_mat")
calc_impact(none_final_03, P3_mat_short, "P3_mat")
calc_impact(none_final_70, P4_mat_short, "P4_mat")
calc_impact(none_final_67, P5_mat_short, "P5_mat")
calc_impact(none_final_67, P6_mat_short, "P6_mat")
calc_impact(none_final_67, P7_mat_short, "P7_mat")
calc_impact(none_final_67, P8_mat_short, "P8_mat")
calc_impact(none_final_high, P9_mat_short, "P9_mat")
calc_impact(none_final_low, P10_mat_short, "P10_mat")

```

# QALY Split
```{r}
## 
base_qaly_split <- none_final$QALY_s$under5
write.csv(base_qaly_split, file = here::here("outputs", "qaly_split", "base.csv"))

calc_impact_split(none_final, base_mab_short, "base_mab")
calc_impact_split(none_final, P1_mab_short, "P1_mab")
calc_impact_split(none_final, P2_mab_short, "P2_mab")

calc_impact_split(none_final_67, base_mat_short, "base_mab")
calc_impact_split(none_final_44, P1_mat_short, "P1_mab")

```
